Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2023-03-10 Thesis/chapter/062-post-emma.tex
proof read post-emma close to finish

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Grid Search, KRR and SVM}
The optimal parameters for each \textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
combination can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took minimum value from the grid search twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
So 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters stimulate regularization and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{ccccccc}
        \hline\hline
        method  &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$)   &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $)   &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$)   &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $)   &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{Best parameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see equations \ref{eq:r2-krr-g}--\ref{eq:r2-svm-p}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$.

\begin{align}
    \label{eq:r2-krr-g}
    R^2(\gamma_{krr}) &= -0.50 \pm 0.25\\
    \label{eq:r2-krr-p}
    R^2(\rho_{krr})   &= -0.45 \pm 0.52\\
    \label{eq:r2-svm-g}
    R^2(\gamma_{svm}) &= -0.37 \pm 0.39\\
    \label{eq:r2-svm-p}
    R^2(\rho_{svm})   &= -0.95 \pm 0.44
\end{align}

%
Finally the \gls{mae} and \gls{mse} were calculated for different data sets with models 
trained on the \gls{emma} data set (see table \ref{tab:post-emma}). 
% EMMA 30 pts
The first two columns show statistics for data the model was trained with and thus, 
these columns contain the lowest numbers. 
% pre-EMMA 21 pts 
The next two columns were calculated with data obtained before the EMMA optimization. 
As the this pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
many data points are outside of the range of the \gls{emma} data set. 
Thus, prediction for this data set are mainly extrapolations. 
% inter/c/ pre-EMMA 5 pts
The next two columns were produced by using pre-\gls{emma} data, 
but only keeping points which sit inside the space spanned by the \gls{emma} constraints. 
It should be expected that these statistics should be lower than in the previous two columns. 
They are higher, though, because of the small sample size of 5 data points. 
% all 51 
The last two columns show data for prediction of all available data. 
These statistics are lower because of the inclusion of the training set in the test set.

In the self test of the first two columns \gls{mars} is the one method to rule them all.
But as soon as unseen data enters the field, linear regression excels with its simplicity. 
The linear regression method is only under cut by when calculating the \gls{mae} of $\gamma$
for the interpolating unseen data with \gls{svm}. 
%
%\todo{could use mean as prediction and compare}
%\todo{could plot pred vs true}
%\todo{pcr}
%\todo{step wise regression}
%\todo{why chose mae and mse}
%\todo{talk about sigma(pred) vs sigma(true)}
%\todo\url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}}
%\todo{\url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}}
%\todo{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)} 
%
\begin{table}[htb]
	\centering
    \caption{Post EMMA vergleich}
	\label{tab:post-emma}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    $\gamma$&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        lin Reg&    13& 250&    24& 747&    34& 1327&   17& 454\\
%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
    $\rho$&  MAEe&   MSEe&   MAEp&   MSEp&   MAEc&   MSEc&   MAEa& MSEa \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        lin Reg&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
\end{table}

>>>>

%\iffalse
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ML %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% GRID SEARACH %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5
\subsection{Grid Search, KRR and SVM}
The optimal parameters for each combination of 
\textit{optimizand} ($\gamma$ and $\rho$) and method (KRR and SVM) 
can be seen in table \ref{tab:grid-search}. 
The parameters are often extrema.
The hyperparameter $\gamma_{ml}$ took the smallest possible value (within the grid search) twice. 
In the polynomial kernel this leads to a lower influence of the input variables with respect to the intercept. 
The range of the hyperparameter $\alpha$ was 0.01--10 in the grid search. 
So, 2 and 10 are high values for the regularization parameter $\alpha$ of \gls{krr}.
The hyperparameter $\varepsilon$ specifies the size of the tube within which data does not contribute to the loss 
and the value 1 is the maximum for $\varepsilon$ during this grid search. 
%\td{why can R2 be negative? https://stats.stackexchange.com/a/279358/374563 } 
%The value 1 for $\varepsilon$ is the highest possible, 
%$C$ is regularization parameter for SVM and $\varepsilon$ is var which defines loss less region in soft margin SVM}
All these extreme values of hyperparameters (stimulate regularization and indicate noisy and difficult to fit data.
\begin{table}
    \center
    \begin{tabular}{cccccccc}
        \hline\hline
        method  &$R^2$   &kernel &degree &$\gamma_{ml}$   &$\alpha$    &$C$    &$\varepsilon$\\
        \hline
        KRR($\gamma$) & $-0.50 \pm 0.25$  &poly   &1  &0.01   &2 &-&-\\
        KRR($\rho  $) & $-0.45 \pm 0.52$  &rbf    &-   &0.2   &10&-&-\\
        SVM($\gamma$) & $-0.37 \pm 0.39$  &poly   &2  &0.5    &-&0.7  &1.0  \\
        SVM($\rho  $) & $-0.95 \pm 0.44$  &poly   &3  &0.01   &-&0.1  &0.1  \\
        \hline\hline
    \end{tabular}
    \caption{$R^2$ values and best hyperparameters for each \textit{optimizand}-method-combination}
    \label{tab:grid-search}
\end{table}
% R2
The $R^2$ values were calculated for each of the models using cross validation. 
Resulting $R^2$ are all below zero (see table~\ref{tab:grid-search}). 
A negative $R^2$ value means that the prediction provided by the model is worse than predicting only the mean of $\gamma$ and $\rho$.

\iffalse
\begin{align}
    \label{eq:r2-krr-g}
    R^2(\gamma_{krr}) &= -0.50 \pm 0.25\\
    \label{eq:r2-krr-p}
    R^2(\rho_{krr})   &= -0.45 \pm 0.52\\
    \label{eq:r2-svm-g}
    R^2(\gamma_{svm}) &= -0.37 \pm 0.39\\
    \label{eq:r2-svm-p}
    R^2(\rho_{svm})   &= -0.95 \pm 0.44
\end{align}
\fi

%
Finally, the \gls{mae} and \gls{mse} were calculated for different data sets 
(see table \ref{tab:post-emma}). 
Each models was trained on the \gls{emma} data set.
% EMMA 30 pts
The first two columns (e) show statistics validated with data the model was trained with (30 data points) and thus, 
these columns contain the lowest numbers. 
% pre-EMMA 21 pts 
The next two columns (p) were calculated with data obtained before the EMMA optimization (21 data points). 
As the pre-optimization data set was mainly used to find appropriate boundaries for the input variables, 
many data points are outside of the range of the \gls{emma} data set. 
Thus, prediction for this data set are mainly extrapolations. 
% inter/c/ pre-EMMA 5 pts
The next two columns (c) were produced by using pre-\gls{emma} data for validation, 
but only keeping points which sit inside the space spanned by the \gls{emma} constraints (5 data points). 
It should be expected that these statistics should be lower than in the previous two columns. 
They are only lower for MARS($\rho$) and LR($\rho$), though. 
This is likely due to the small sample size.
% all 51 
The last two columns show data for predictions of all available data (51 data points). 
These statistics are lower because of the inclusion of the training set in the test set.

In the self test of the first two columns \gls{mars} is the one method to rule them all and provides the lowest metrics.
But as soon as unseen data enters the field, linear regression excels by its simplicity. 
\td{The linear regression method is only under cut by \gls{svm} when calculating the \gls{mae} of $\gamma$}
for the interpolating unseen data (c).
%
%\todo{could use mean as prediction and compare}
%\todo{could plot pred vs true}
%\todo{pcr}
%\todo{step wise regression}
%\todo{why chose mae and mse}
%\todo{talk about sigma(pred) vs sigma(true)}
%\todo\url{https://blog.minitab.com/en/adventures-in-statistics-2/regression-smackdown-stepwise-versus-best-subsets}}
%\todo{\url{https://blog.minitab.com/en/how-to-choose-the-best-regression-model}}
%\todo{do regression for avg(-log(G)) instead of $\gamma$=avg( ( 13+log(G))**2)} 
%
\begin{table}[htb]
	\centering
%    \caption{Post EMMA vergleich}
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\gamma$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   10& 171&    28& 1084&   30& 1280&   17& 548\\
        LR&    13& 250&    24& 747&    34& 1327&   17& 454\\
%        KRR& 15& 415&    26& 1048&   28& 1586&   19& 676\\
        KRR &17 &548 &30 &1477 &35 &2167 &23 &931\\
        SVM& 15&  415&    26& 1050&   28& 1588&   19& 677\\
        \hline
%    \hline\hline
	\end{tabular}
    %
	\begin{tabular}{c cc cc cc cc}
    \hline\hline
        $\rho$&  MAE(e)&   MSE(e)&   MAE(p)&   MSE(p)&   MAE(c)&   MSE(c)&   MAE(a)& MSE(a) \\
    \hline
        MARS&   0.14&   0.03&   0.41&   0.21&   0.39&   0.18&   0.25&   0.11\\
        LR&    0.19&   0.06&   0.30&   0.15&   0.38&   0.13&   0.24&   0.09\\
%        KRR& 0.30&   0.22&   0.47&   0.38&   0.52&   0.44&   0.34&   0.26\\
        KRR &0.25 &0.12 &0.38 &0.24 &0.43 &0.29 &0.31 &0.17\\
%        SVM& 0.28&   0.12&   0.37&   0.21&   0.42&   0.25&   0.32&   0.16\\
        SVM &0.23 &0.13 &0.41 &0.28 &0.45 &0.33 &0.31 &0.20\\
    \hline\hline
	\end{tabular}
    \caption{Comparison of MAE and MSE of different prediction methods for different data sets: EMMA data set~(e), pre-EMMA data set~(p), pre-EMMA data set within EMMA bounds~(c) and complete dataset~(a)}
	\label{tab:post-emma}
\end{table}
